### 2020-05-26 writeup/experiments.tex
sec 3

{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}\footnote{We also tested with multi-layer perceptron and CNN. The results are similar (cf. Appendix \ref{label:real_result_details}).}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

@@

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{LSTM (averaged)}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{MLP (averaged)}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{LSTM for one pair}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size.}
	\label{fig_covariate}
\end{figure}

>>>>

{For each task, the goal is to categorize sentiment opinions expressed in the text.
We use an embedding layer (with GloVe embeddings\footnote{http://nlp.stanford.edu/data/wordvecs/glove.6B.zip}) followed by an LSTM layer proposed by~\cite{lei2018simple}.
}
%multi-layer perceptron (MLP), LSTM, CNN on all tasks
%We use this task to verify our theoretical results on model capacity and task covariance in real world.

@@

\begin{figure}[!ht]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Averaged}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_trec_cr_lstm.pdf}
		\caption{Task pair TREC and CR}
	\end{subfigure}\hfill
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_mr_sst_lstm.pdf}
		\caption{Task pair MR and SST}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size.}
	\label{fig_covariate}
\end{figure}
